Geometric variational problems

### 2020-11-10 NSF2020/Description/specificaim1_ver2.tex
Update specificaim1_ver2.tex

We will develop some of the mathematical connections between the HAP energy and the energy functional used in the phase field method. 
The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
The approximation becomes sharp in the zero interfacial thickness limit and minimizers of the phase field functional converge (after normalization) 
to the characteristic function of a set solving a perimeter minimization problem 
\cite{The Gradient Theory of Phase Transitions and the Minimal lnterfaee Criterion, }. 
Analogously, the HAP energy converges to the surface energy in the limit
$\rho \to 0$, and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
area measures supported on the particle boundaries. We will use boundary layer analysis to study the rate
of convergence as it depends on \cite{Stephan Luckhaus & Luciano Modica, LeeRyham}

>>>>

We will develop some of the mathematical connections between the HAP energy and the energy functionals used in the gradient theory of phase transitions. 
The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
The approximation becomes sharp in the zero interfacial thickness limit and minimizers of the phase field functional converge (after normalization) 
to the characteristic function of a set solving a perimeter minimization problem 
\cite{The Gradient Theory of Phase Transitions and the Minimal lnterfaee Criterion, 
The Gradient Theory of Phase Transitions and the Minimal Interface Criterion. Arch. Rational Mech. Anal. 98 (1986) 123–142.
L. Modica, Gradient Theory of Phase Transitions with Boundary Contact Energy. Ann. Inst. H. Poincaré, Analyse Nonlinéaire, 4 (1987) 487–512.}.

Analogously, the HAP energy converges to the surface energy in the limit of vanishing screening length 
and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
area measures supported on the particle boundaries. 
PI RR has worked directly on phase field approximations of membrane bending energy \cite{Willmore} and asymptotcs in the Poisson-Boltzman equation \cite{LeeRyham}.
The proposed analysis is a natural outgrowth or prior work because the linearization of the Poisson-Boltzmann equation is the screened Laplace equations \eqref{SL}.
One of the basic questions is to establish the HAP convergence rate as a function of particle geometry 
\cite{Stephan Luckhaus & Luciano Modica}, which is an essential benchmark for numerical validation. 
In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  
As an illustration, consider two fluid-bound plates $P_1$ and $P_2$ that geometrically flat and hydrophobic all sides.
We conjecture that in the zero-screening length limit, the plates have overlapping faces, and that 
\begin{equation}
\lim_{\rho \to 0} \min \Phi_{\text{hydro}} = \max_{\mathcal{X}} A(P_1 \Delta P_2)
\end{equation}
$A(P_1 \Delta P_2)$ is the area of the symmetric difference of the overlap.
